% !TEX root = ../main.tex
%
\chapter{Appendix}
\label{sec:appendix}

\todo{bring both questionnaires into the same format}

\section{Interview Questions}
\label{sec:appendix:interview-questions}

\textbf{Introduction}
\begin{itemize}
\item Thank the interviewee for their participation.
\item Briefly explain the purpose of the interview, which is to gather insights for the development of a NeRF interface.
\item Assure the interviewee that their responses will be kept confidential.
\end{itemize}

\textbf{Background}
\begin{itemize}
\item Can you briefly describe your experience with NeRF or 3D modeling in general?
\end{itemize}

\textbf{Needs and Challenges}
\begin{itemize}
\item What specific tasks or objectives do you typically aim to achieve when working with NeRF models or 3D scenes?
\item What are the main challenges or pain points you encounter when using current NeRF frameworks or interfaces?
\end{itemize}

\textbf{Usability and Features}
\begin{itemize}
\item In your opinion, what features or functionalities would make a NeRF interface most useful for your work or research?
\item Are there any specific editing or manipulation tools you find lacking in current NeRF interfaces?
\item How important is real-time visualization and interactivity in a NeRF interface for your needs?
\end{itemize}

\textbf{Ease of Use}
\begin{itemize}
\item How do you envision the ideal user interface for NeRF? What elements would make it easy to use, even for those with limited technical expertise?
\item What level of technical knowledge or familiarity with 3D modeling should the ideal NeRF interface require from its users?
\end{itemize}

\textbf{Integration and Compatibility}
\begin{itemize}
\item Are there any other software tools or workflows you typically use alongside NeRF, and how important is it for a NeRF interface to integrate with these tools?
\item Do you have any preferences regarding the file formats or data compatibility that the NeRF interface should support?
\end{itemize}

\textbf{Feedback and Suggestions}
\begin{itemize}
\item Are there any additional thoughts, suggestions, or requirements you would like to share regarding the development of a NeRF interface?
\item Is there anything else you believe is essential for us to understand about your needs and expectations?
\end{itemize}

\textbf{Closing}
\begin{itemize}
\item Thank the interviewee for their time and valuable input.
\item Provide contact information for any follow-up questions or clarifications.
\end{itemize}

\section{User Study Questionnaire}
\label{sec:appendix:questionnaire}

\textbf{Usability Experience}
\begin{itemize}
\item Can you share your overall impressions of using the Simplify NeRF application?
\item Were there any specific features or functionalities of the application that stood out to you positively? If so, why?
\item On the other hand, were there any aspects of the application that you found challenging or frustrating? Please elaborate.
\end{itemize}

\textbf{Task-Specific Feedback}
\begin{itemize}
\item Were there any particular steps or actions within the tasks that you found confusing or unclear? If yes, could you describe them?
\item Were there any features or functionalities you expected to find in the application that were missing? If so, what were they?
\end{itemize}

\textbf{Suggestions for Improvement}
\begin{itemize}
\item Based on your experience using the Simplify NeRF application, do you have any suggestions for improving its usability or functionality?
\item Are there any specific changes or enhancements you would like to see in future versions of the application?
\item How do you think the application could better meet your needs or expectations as a user?
\end{itemize}

\textbf{Closing}
\begin{itemize}
\item Is there anything else you would like to add or share about your experience with the Simplify NeRF application?
\item Thank the participant for their time and valuable feedback.
Offer contact information for any follow-up questions or clarifications.
\end{itemize}


\section{User Testing Results}
\label{sec:appendix:testing-results}

\section{Prototype Documentation}
\label{sec:appendix:prototype-doc}

