% !TEX root = ../main.tex
%
%************************************************
% Declaration
%************************************************
\pdfbookmark[0]{Declaration}{Declaration}
\chapter*{Declaration of Honor}
\label{sec:declaration}
\thispagestyle{empty}

\vspace*{-10mm}

I do solemnly declare that I prepared this thesis independently and that the thoughts taken directly or indirectly from other sources are indicated accordingly.
The work has not been submitted to any other examination authority and also not
yet been published.

\bigskip

\noindent\textit{\thesisUniversityCity, \thesisDate}

\smallskip

\begin{flushright}
	\begin{minipage}{5cm}
		\rule{\textwidth}{1pt}
		\centering\thesisName
	\end{minipage}
\end{flushright}

\vspace*{10mm}

{\usekomafont{chapter}Declaration of AI Usage} \\

I declare that I have exclusively used ChatGPT 4\footnote{https://chat.openai.com}, Whisper\footnote{https://github.com/openai/whisper}, DeepL Write\footnote{https://www.deepl.com/write} and MAXQDA's AI Assist\footnote{https://www.maxqda.com/products/ai-assist} in my thesis for the purposes listed below:

\begin{itemize}
	\item Transcription of Interviews.
	\item Summarizations of Research Papers.
	\item Correction of grammar, proofreading and editing.
	\item Brainstorming of thesis structure and content.
\end{itemize}

Prompts are available in the AI Usage Reflection.
I confirm that I have checked my thesis and its text for unintended plagiarism and that I have verified all facts and references used from the ChatGPT output.

\bigskip

\noindent\textit{\thesisUniversityCity, \thesisDate}

\smallskip

\begin{flushright}
	\begin{minipage}{5cm}
		\rule{\textwidth}{1pt}
		\centering\thesisName
	\end{minipage}
\end{flushright}

%*****************************************
%*****************************************
